Numerical simulations of the Cordilleran ice sheet through the last glacial cycle

### 2014-07-18 cordillera-cycle.tex
Latex2rtf compatibility changes.

@@

% Copernicus discussion paper
%\documentclass[tcd, hvmath, online]{copernicus}

% Copernicus-like latex2rtf compatible
%\input{copernicus_rtf}

@@

\renote{
    Surface mass balance is the balance of mass fluxes at the surface,
    consisting of ice accumulation and ice ablation, which I introduce straight
    away. I don't see what kind of ``opening sentence'' can be added here.}
Ice surface accumulation and ablation are computed from monthly mean
near-surface air temperature, $T_m$, monthly standard deviation of near-surface
air temperature, $\sigma$, and monthly precipitation, $P_m$, using
a~temperature-index model \citep[e.g.,][]{Hock.2003}. Accumulation is equal to
precipitation when air temperatures are below 0\,\unit{{\degree}C}, and
decreases to zero linearly with temperatures between 0 and
2\,\unit{{\degree}C}. Ablation is computed from the number of positive
degree-days (PDD), defined as the integral of temperatures above
0\,\unit{{\degree}C} in one year.

@@

% =============================================================================
\section[Comparison to the geologic record]
        {Comparison to the geologic record\renote{
    Arjen has proposed: 2.1 Evaluation of model runs agains field evidence, 2.2
    Palaeoglaciology of the Cordilleran ice sheet, and 2.3 The last
    deglaciation; but I don't think that these headers work. In my view, this
    entire ``discussion'' part is all about evaluation of model runs agains
    field evidence and palaeoglaciology. It is necessary that this comparison
    starts here, in order to ``kick out'' the records that perform badly (ODP*,
    NGRIP) and justify that the rest of the analysis is performed on two
    (high-resolution) simulations only. Such figures as
    Figs.~\ref{fig:duration}--\ref{fig:warmfrac} and Fig.~\ref{fig:deglac},
    which I consider as different views of the results rather than new results
    (apart the fact that they use higher resolution) are drawn for the purpose
    of comparing model results against geological evidence. I propose to rename
    this section to a more explicit ``Comparison to the geologic record'' (or
    similar). I have also renamed the ``results'' to ``Sensitivity to
    atmospheric forcing time-series'', which is actually what that section is
    about: raw model output, no discussion against the geologic record. This
    new discussion is divided in three parts: 4.1 Glacial maxima, where we
    study the maximum stages, relatively well-documented by the geology; 4.2
    Nucleation centres, where we study ``intermediate'' states, for which less
    is known, but the model can say something; and 4.3 The last deglaciation,
    which deserves a separate section because many people are interested in
    this period, and much geological evidence is available.}}
\label{sec:discussion}
% =============================================================================

>>>>

% Copernicus-like latex2rtf compatible
\newif\iflatextortf
\iflatextortf
\input{copernicus_rtf}
\else

@@

% Copernicus discussion paper
%\documentclass[tcd, hvmath, online]{copernicus}
\fi

@@

Ice surface accumulation and ablation are computed from monthly mean
near-surface air temperature, $T_m$, monthly standard deviation of near-surface
air temperature, $\sigma$, and monthly precipitation, $P_m$, using
a~temperature-index model \citep[e.g.,][]{Hock.2003}\renote{
    Surface mass balance is the balance of mass fluxes at the surface,
    consisting of ice accumulation and ice ablation, which I introduce straight
    away. I don't see what kind of ``opening sentence'' can be added here.}.
Accumulation is equal to
precipitation when air temperatures are below 0\,\unit{{\degree}C}, and
decreases to zero linearly with temperatures between 0 and
2\,\unit{{\degree}C}. Ablation is computed from the number of positive
degree-days (PDD), defined as the integral of temperatures above
0\,\unit{{\degree}C} in one year.

@@

% =============================================================================
\section{Comparison to the geologic record}
\label{sec:discussion}
% =============================================================================

\emph{[\textbf{About the new titles}: In my view, this
    entire ``discussion'' part is all about evaluation of model runs agains
    field evidence and palaeoglaciology. It is necessary that this comparison
    starts here, in order to ``kick out'' the records that perform badly (ODP*,
    NGRIP) and justify that the rest of the analysis is performed on two
    (high-resolution) simulations only. Such figures as
    Figs.~\ref{fig:duration}--\ref{fig:warmfrac} and Fig.~\ref{fig:deglac},
    which I consider as different views of the results rather than new results
    (apart the fact that they use higher resolution) are drawn for the purpose
    of comparing model results against geological evidence. I propose to rename
    this section to a more explicit ``Comparison to the geologic record'' (or
    similar). I have also renamed the ``results'' to ``Sensitivity to
    atmospheric forcing time-series'', which is actually what that section is
    about: raw model output, no discussion against the geologic record. This
    new discussion is divided in three parts: 4.1 Glacial maxima, where we
    study the maximum stages, relatively well-documented by the geology; 4.2
    Nucleation centres, where we study ``intermediate'' states, for which less
    is known, but the model can say something; and 4.3 The last deglaciation,
    which deserves a separate section because many people are interested in
    this period, and much geological evidence is available.]}
